pirouette: Determining the error BEAST2 makes in inferring a phylogeny

### 2019-03-07 article.tex
Example research question 1 peeks ahead at twinnning

\begin{lstlisting}[
    language=R, floatplacement=ht, frame=single, 
    label = {lst:create_yule_tree}, 
    caption = {Create a Yule tree}
  ]
phylogeny <- create_yule_tree(n_taxa = 6, crown_age = 10)
\end{lstlisting}

\begin{figure}[ht]
  \includegraphics[width=\textwidth]{figure_bd.png}
  \caption{The Yule tree, as created by listing \ref{lst:create_yule_tree}}
\end{figure}

@@

>>>>

\begin{lstlisting}[
    language=R, floatplacement=ht, frame=single, 
    label = {lst:create_yule_tree}, 
    caption = {
      Create a Yule tree. 
      The resulting tree is shown in figure \ref{fig:yule_tree}
    }
  ]
phylogeny <- create_yule_tree(n_taxa = 6, crown_age = 10)
\end{lstlisting}

\begin{figure}[ht]
  \includegraphics[width=\textwidth]{tree_yule.png}
  \caption{The Yule tree, as created by listing \ref{lst:create_yule_tree}}
  \label{fig:yule_tree} 
\end{figure}

@@

The error distribution obtained in this way can serve as a control:
imagine one develops a novel tree prior related to the Yule model.
One can predict that BEAST2 will be worse in recovering the phylogenies
from that novel tree prior, as only the existing tree priors are used
in inference. 
To determine how much worse the recovery is, one needs to know the 
inference error made by existing tree priors. 
As this control is important, it is an inherent part of \verb;pirouette;:
it is called twinning, which is shown in example research question 3.
